A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-12 docs/methods/erosion_methods.tex
NM

Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.  In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on. Such processes of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow~\cite{hewett2017evolution}. From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, since the medium is composed of many individual constituents, multi-body interactions must be considered. Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.
% in particular close-contacts?

>>>>

Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and during related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.  In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on. Such examples of `sculpting with flow'~\cite{ristroph2018sculpting} have been examined in the context of a single body~\cite{ris-moo-chi-she-zha2012, moore2017riemann} and, more recently, multiple bodies whose shape evolution is coupled through the flow~\cite{hewett2017evolution}. From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, since the medium is composed of many individual constituents, multi-body interactions must be considered. Second, the tight-packing present in many porous-media applications means that close-contacts must be resolved. Finally, long-range effects inherent to Stokes flow couples the shape evolution of {\em all} bodies, more so than in any other flow regime.

% close contact, close proximity, nearby
